Optimal (Multiway) Spatial Joins

### 2024-05-24 msj.tex
yufei

\begin{lemma} \label{lmm:hv:type1:cross-non-empty}
    Suppose that $r_1, r_2, ..., r_{k-2}$ are the full rectangles of $r_1', r_2', ..., r_{k-2}'$, respectively. All the following statements are true:
    \myenums{
        \item $\cross(\bm{t}, H) \ne \emptyset$ and $\cross(\bm{t}, V) \ne \emptyset$.
    }
\end{lemma}

>>>>

\begin{lemma} \label{lmm:hv:type1:cross-non-empty}
    Let $r_i$ be the full rectangle of $r_i'$ for each $i \in [k-2]$. All the following statements are true:
    \myenums{
        \item $\cross(\bm{t}, H) \ne \emptyset$ and $\cross(\bm{t}, V) \ne \emptyset$.
        \item For any $h \in \cross(\bm{t}, H)$ and $v \in \cross(\bm{t}, V)$, the $k$-tuple $(r_1, r_2, ..., r_{k-2}, h, v)$ belongs to $\J(R_1, ..., R_{k-2}, H, V)$.
        \item If a $k$-tuple $(r_1, r_2, ..., r_{k-2}, h, v)$ belongs to $\J_1$, then $h \in \cross(\bm{t}, H)$ and $v \in \cross(\bm{t}, V)$.
    }
\end{lemma}
